Modelling the Trojan Asteroids

### 2020-04-20 Report/draft1.tex
lagrange_stability completed

\subsection{Performance}
Sampling 100 points per orbit for 100 orbits takes a mean time of 0.01723 seconds \textbf{(add error?)}, with sub-linear scaling for sampling rate and orbit number up to the array memory limit, achieved through the optimised integration routines within solve\_ivp.

@@

>>>>

\subsection{Performance}
Sampling 100 points per orbit for 100 orbits takes a mean time of $16.97 \pm 34$ \si{\milli\second} \textbf{(add error?)}, with sub-linear scaling for sampling rate and orbit number up to the array memory limit, achieved through the optimised integration routines within solve\_ivp.

@@

In the stationary frame, this wander from the (now moving) Lagrange point is depicted in Figure \ref{fig:greeksdeviationstationaryframe}. The deviation oscillates with a magnitude of $9.10 \times 10^{-2}$ AU, and a period of $148.2 \pm 0.8$ years, where the error was determined by the width of the Fourier peak. This is modulated with a faster oscillation component of $11.85 \pm 0.27$ years, equivalent to the orbital period of the asteroids and clearly demonstrating an periodic error in the integration routine, becoming more significant over time.

These much more significant errors are due to \textbf{YYY}. Energy can also be evaluated, and conserved, in this inertial frame; asteroid specific energy varies within only 0.113\% of the initial value, and with a similar periodicity to wander.

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{Figures/greeks_deviation_stationary_frame}
	\caption[]{The wander of Greek asteroids from the Lagrange point in the stationary frame. Note the two oscillation components and constant maximum oscillation amplitude over time, demonstrating this point is indeed stable. }
	\label{fig:greeksdeviationstationaryframe}
\end{figure}

Animations show orbit....
